---
title: "Workshop on 'Reproducible Research in Python"
author: ""
site: bookdown::bookdown_site
output: 
    bookdown::gitbook:
        css: style.css
        number_sections: false
        anchor_sections: false
        split_by: chapter
        config:
            sharing:
                 github: no
                 facebook: no
                 twitter: no
                 all: no
            toc:
                collapse: section
                scroll_highlight: yes
                before: <li class="toc-logo"><a href="./"></a> <h4 class=".paddingtitel ">RePresInPython</h2></li>
header-includes:
  - \usepackage{fontawesome5}
---

```{r include = FALSE}
# Define the web addresses for the course
# run as needed, not included automatically because of stuff (aka git complains)
githuburl <- "https://github.com/DataScienceILC/repres-with-python"
readerurl <- ""
email <- "marc.teunis@hu.nl"

save(
    list = c("githuburl", "readerurl", "email"), 
    file = "course_urls.RData")
```


```{r include = FALSE, eval = TRUE}
# set CSS for objects
knitr::opts_chunk$set(
  class.source="Rchunk", 
  class.output="Rout", 
  warning = FALSE,
  error = FALSE,
  message = FALSE)
```

# Introduction {-}

Download the source code [`r icons::fontawesome("github")`](https://github.com/DataScienceILC/repres-with-python)


This reader contains a number of workflows and instructions on how to setup a complete programming environment for working with Python

The steps include:

 1. Organize your work and files and think about naming conventions, where to store which files and how to manage scripts, data and meta-data. This is decribed in the [Guerilla Analytics documentation]()
 2. 
